%-------------------------
% Resume in Latex for Jack Sparrow
% Author : Le Chat
% Based on: Cool Looking Template by Wilmer Gonzalez
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{pagecolor}
\usepackage{lato}
\usepackage{fontawesome}

% Page styling
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
  \textbf{#1:} #2
}

% Dark theme
\colorlet{textcolor}{white!80!gray}
\colorlet{backgroundcolor}{black!30!gray}
\colorlet{urlcolor}{blue!25!white}
\AtBeginDocument{\color{textcolor}}

% Document
\begin{document}
\pagecolor{backgroundcolor}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://en.wikipedia.org/wiki/Jack_Sparrow}{\Large Captain Jack Sparrow}} & \faicon{ship} \color{urlcolor} The Black Pearl \\
  \href{mailto:jack.sparrow@eitc.gov}{jack.sparrow@eitc.gov} & \faicon{compass} Navigator, Strategist \\
  \textsl{\small \"The problem is not the problem. The problem is your attitude about the problem.\"} & \textsl{\small \href{https://en.wikipedia.org/wiki/Pirates_of_the_Caribbean}{Pirates of the Caribbean}}
\end{tabular*}

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {East India Trading Company}{Caribbean Sea}
      {Freelance Consultant (Formerly Wanted)}{1720 - Present}
      \resumeItemListStart
        \resumeItem{Outmaneuvered the British Royal Navy and Davy Jones to regain control of the \textbf{Black Pearl}, demonstrating unparalleled negotiation and tactical skills.}
        \resumeItem{Recruited and led a diverse crew of misfits, proving expertise in team management under extreme conditions.}
        \resumeItem{Navigated uncharted waters using only a broken compass, showcasing adaptability and resourcefulness.}
      \resumeItemListEnd
      \resumeTech{Skills}{Swordsmanship, Cartography, Rum Tasting, Escape Artistry.}

    \resumeSubheading
      {Pirate Lord of the Caribbean}{Tortuga, Caribbean}
      {Self-Employed}{1710 - Present}
      \resumeItemListStart
        \resumeItem{Acquired and lost the \textbf{Black Pearl} multiple times, demonstrating resilience and persistence.}
        \resumeItem{Negotiated with supernatural entities, including Davy Jones and Calypso, to secure favorable outcomes.}
        \resumeItem{Developed a reputation for \"creative interpretations\" of the Pirate Code, emphasizing flexibility in legal frameworks.}
      \resumeItemListEnd
      \resumeTech{Tools}{Compass (mysteriously points to what you want most), Pistols, Rum.}

    \resumeSubheading
      {The Flying Dutchman}{Seven Seas}
      {Temporary Crew Member}{1729 - 1729}
      \resumeItemListStart
        \resumeItem{Briefly served under Davy Jones to settle a debt, gaining firsthand experience in cursed naval operations.}
        \resumeItem{Played a key role in the mutiny against Davy Jones, leading to his eventual freedom.}
      \resumeItemListEnd
      \resumeTech{Skills}{Survival, Crisis Management, Kraken Evasion.}

    \resumeSubheading
      {Port Royal Governor's Office}{Port Royal, Jamaica}
      {Consultant (Unofficial)}{1725 - 1728}
      \resumeItemListStart
        \resumeItem{Assisted in the rescue of Elizabeth Swann from cursed Aztec gold, proving expertise in risk assessment.}
        \resumeItem{Escaped execution through a combination of wit, luck, and a well-timed lunar eclipse.}
      \resumeItemListEnd
      \resumeTech{Achievements}{Avoided hanging, acquired eternal fame.}

\resumeSubHeadingListEnd

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {School of Hard Knocks}{Caribbean Sea}
      {Master of Pirate Arts}{Self-Taught}
      \resumeItemListStart
        \resumeItem{Studied under legendary pirates, including Captain Teague (allegedly).}
        \resumeItem{Specialized in improvisation, deception, and rum-based diplomacy.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% SKILLS
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Navigation:} Expert in celestial navigation, dead reckoning, and \"going where the wind takes me.\"}
    \resumeSubItem{\textbf{Languages:} Fluent in English, Pirate, and sarcasm.}
    \resumeSubItem{\textbf{Combat:} Proficient in swordplay, hand-to-hand combat, and dramatic escapes.}
    \resumeSubItem{\textbf{Leadership:} Inspired loyalty in crews through charisma and questionable promises.}
  \resumeSubHeadingListEnd

% CERTIFICATIONS
\section{Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brethren Court}{Shipwreck Cove}
      {\href{https://en.wikipedia.org/wiki/Pirate_lord}{Pirate Lord}}{1750}
    \resumeSubheading
      {Royal Navy}{Port Royal}
      {\href{https://en.wikipedia.org/wiki/Letter_of_marque}{Letter of Marque (Revocable)}}{1718}
  \resumeSubHeadingListEnd

% NOTABLE ACHIEVEMENTS
\section{Notable Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{Stole the \textbf{Black Pearl} from Captain Hector Barbossa using only a small boat and sheer audacity.}
    \resumeSubItem{Survived the \textbf{Kraken}, the \textbf{Flying Dutchman}, and multiple hangings.}
    \resumeSubItem{Discovered the \textbf{Fountain of Youth} (but lost the map).}
    \resumeSubItem{Star of the \textbf{Pirates of the Caribbean} franchise (unpaid).}
  \resumeSubHeadingListEnd

% REFERENCES
\section{References}
  \resumeSubHeadingListStart
    \resumeSubItem{\textbf{Captain Hector Barbossa} - \"He's a dreadful pirate, but you'd be surprised how often he escapes.\"}
    \resumeSubItem{\textbf{Elizabeth Swann} - \"Complicated, but effective.\"}
    \resumeSubItem{\textbf{Will Turner} - \"I owe him a ship.\"}
  \resumeSubHeadingListEnd

\end{document}